---
title: "Youtube Trends Project"
author: "Ghassen YAHIA"
date: "25/03/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analyze YouTube Trends with a Dashboard
YouTubers are faced with the pressure to create content that can potentially become viral and help pave their way to be the Internet’s next sensation.

What, then, gets more views nowadays? 
Are certain categories more popular than others in general, or does title length matter too?

## Setting Up the Environment
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Reading Data from the CSV File
```{r}
setwd("/home/gyahia/Documents/Portfolio/RStudio/CognitiveClass/Youtube_Project/")
video_stats <- read.csv("videos-stats.csv")
```

## Information about the dataset
### First glance at the dataset
```{r}
#  video_stats
```
### Checking Dimensions
It will give the number of OBSERVATIONS first (rows) and the number of VARIABLES after (columns)
```{r}
dim(video_stats)
```


### Two different ways of summarizing the dataset
```{r}
str(video_stats)
summary(video_stats)
```

### Checking for any N/A values
```{r}
video_stats %>%
    summarise_all(~ sum(is.na(.)))
```
There are two N/A Values for variables Likes, Comments an views.

### Dropping these values from the dataset.
```{r}
video_stats <- video_stats %>%
    drop_na()
```

### Checking for duplicates
```{r}
any(duplicated(video_stats, ))
video_stats[duplicated(video_stats), ]
```
No duplicate rows found in the dataset.

If we want to look for duplicates depending on one or multiple variable we can look ccheck it this way.
```{r}
# any(duplicated(video_stats$Keyword))
# video_stats[duplicated(video_stats$Keyword),]
```

## Data Manipulation
### Creating new variables more pertinent to the job at hand

### Checking performance of videos per 1K views in terms of Likes and Comments  
```{r}
video_stats <- video_stats %>%
    mutate(
        LikesPer1k = round(Likes / (Views / 1000), 2),
        CommentsPer1k = round(Comments / (Views / 1000), 2)
    )
video_stats <- video_stats %>%
    mutate(PubYear = as.factor(substr(Published.At, 1, 4)))

glimpse(video_stats)
```
## Creating Plots
In this case we want to see the numbeer of published videos per year.
We will be using one variable that is discrete for the plotting PubYear.
In this scenarion geom_bar is the best way to go.
```{r}
video_stats %>%
    ggplot(aes(x = PubYear)) +
    geom_bar(fill = "blue") +
    theme_minimal() +
    labs(
        title = "Number of videos per year",
        x = "Publication year", y = "Count of videos"
    )
```



```{r}
group_keyword_avg_likes_views <- video_stats %>%
    group_by(Keyword) %>%
    summarise(
        avg_likes_in_K = mean(Likes, na.rm = FALSE) / 1000,
        avg_views_in_K = mean(Views, na.rm = FALSE) / 1000, count = n()
    )
print(
    arrange(group_keyword_avg_likes_views, desc(avg_likes_in_K)),
    n = 25
)
```
Mr Beast is the one getting the most number of likes even though hehas not the biggest number of average 
views.   


```{r}
group_keyword_avg_likes_views_year <- video_stats %>%
    group_by(Keyword, PubYear) %>%
    summarise(
        avg_likes = mean(Likes, na.rm = FALSE),
        avg_views = mean(Views, na.rm = FALSE), count = n()
    )
print(
    arrange(group_keyword_avg_likes_views_year, desc(avg_likes)),
    n = 25
)
```

Depending on the year, some Keywords got more likes than MrBeast videos on average.
```{r}
summary(group_keyword_avg_likes_views)
```
Maximum count is 50 and Max Avg Views is :103365  (in Thousands).
```{r}
coeff_avg_views_vs_count <- max(group_keyword_avg_likes_views$count) /
    max(group_keyword_avg_likes_views$avg_views_in_K)
```

```{r fig.width=20, fig.height=10}
legend_colors <- c("blue", "red")
legend_labels <- c("Count", "AVG Views (in Thousands)")

# Plot count and average views by keyword
ggplot(group_keyword_avg_likes_views, aes(x = Keyword)) +
    # Add first y-axis with count
    geom_bar(aes(y = count, fill = legend_colors[1]),
        stat = "identity",
        width = 0.4, position = position_nudge(x = 0.15)
    ) +
    # Add second y-axis with average views
    geom_bar(aes(y = avg_views_in_K / 1000, fill = legend_colors[2]),
        stat = "identity",
        width = 0.4, position = position_nudge(x = -0.15)
    ) +
    # Add a legend
    scale_fill_manual(values = legend_colors, labels = legend_labels) +
    # Add a title and adjust theme
    ggtitle("\n Count and Average Views by Keyword\n") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, size = 15),
         text = element_text(size = 20)) +
    scale_y_continuous(
        name = "Count\n",
        sec.axis = sec_axis(~ . / coeff_avg_views_vs_count,
         name = "AVG Views (in Thounsands)\n")
    )
  ```

Even though some categories have the same number of videos available, the number of likes is way too divergent for 5 of them.

Keywords having more than 10000000 AVG Views.
```{r}
most_viewed_channels <- group_keyword_avg_likes_views %>%
    filter(avg_views_in_K > 10000) %>%
    arrange(desc(avg_views_in_K))

most_viewed_channels

legend_labels2 <- c("AVG Likes (in Thousands)", "AVG Views (in Thousands)")


ggplot(most_viewed_channels, aes(x = Keyword)) +
    # Add first y-axis with count
    geom_bar(aes(y = avg_likes_in_K, fill = legend_colors[1]),
        stat = "identity",
        width = 0.4, position = position_nudge(x = 0.2)
    ) +
    # Add second y-axis with average views
    geom_bar(aes(y = avg_views_in_K / 1000, fill = legend_colors[2]),
        stat = "identity",
        width = 0.4, position = position_nudge(x = -0.2)
    ) +
    # Add a legend
    scale_fill_manual(values = legend_colors, labels = legend_labels2) +
    # Add a title and adjust theme
    ggtitle("\n Average Views/Likes by Keyword\n") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90),
         text = element_text(size = 10)) +
    scale_y_continuous(
        name = "AVG Views (in Thounsands)\n",
        sec.axis = sec_axis(~ . / 50, name = "AVG Likes (in Thounsands)\n")
    )
```


